Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-02 snapshot_system/eval1.tex
updated plots

Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
nodes fail for different amounts of sharing of filesystem blocks in the index. We
show 5 and 20 for the VO and VC block links counts because those are what we
measured in our small dataset, and chose higher numbers to account for much
larger datasets. We chose to use a very optimistic setting for VO (20), and the
absolute worst case amount of sharing for VC in a 100 machine cluster with 25
VMs per machine (2500). Our results show that even the VC worst case provides
better VM reliability that VO. As you can see from the graph, even small
changes in the number of links to VO blocks has a significant impact on
reliability, while even a 50 times increase in the VC block link counts only
slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig:pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher PDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

@@

@@

		title={\small $p=100000$},

@@

		extra y ticks={99.99}, %if important numbers are missing

@@

                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_100000.txt};

@@

                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_100000.txt};

@@

                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_100000.txt};

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig:pds-replication}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig:pds-replication2}
\end{figure}

@@

%graph comparing extreme binning (SRB) with PDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            cycle list name=mline,
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north},
            ]
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    SRB and  VC.}
  \label{fig:exbin-efficiency-graph}
\end{figure}

%version of above graph using minhash algorithm
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            cycle list name=mline,
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north},
            ]
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC. VC uses the minhash algorithm for Level-2.}
  \label{fig-exbin-efficiency-graph2}
\end{figure}

>>>>

Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
nodes fail for different amounts of sharing of filesystem blocks in the index.
We show 6.3 for the VO sharing because that is what we measured in our dataset,
and while we expect it to continue to grow (thereby decreasing fault
tolerance), it should do so slowly, so we treated VO FSB sharing as a
contstant factor of 6.3, as it doesn't change our results. for VC we use 1250, because that is what we
estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
2500 VMs sharing each PDS FSB because that is the absolute worst case for 2500
VMs. Our results show that even the VC worst case provides better VM
reliability than our optimistic amount of sharing in VO. 
The key factor placed is that  $N_1 +N_2 <
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig:pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. We
use our estimate of 1250 VMs sharing each PDS block, which is what we expect
for 2500 VMs, given the growth up to 105 VMs. It is easy to see though thatr
increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. Increasing the
PDS replication is cheap because is makes up a very small percent of the
stored data, but the impact is significant. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

@@

            \pgfplotsset{/pgf/number format/.cd,
                fixed,precision=4}

@@

		title={\small $p=1000$},

@@

		%extra y ticks={99.99}, %if important numbers are missing

@@

                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};

@@

                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};

@@

                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.7\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig:pds-replication}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.7\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig:pds-replication2}
\end{figure}

@@

\comments{%superceded by minhash algorithm (below)
%graph comparing extreme binning (SRB) with PDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            cycle list name=mline,
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north},
            ]
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    SRB and  VC.}
  \label{fig:exbin-efficiency-graph}
\end{figure}
}

%version of above graph using minhash algorithm
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.7\linewidth,
            cycle list name=mline,
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=88.5,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny},
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            \legend{SRB,VC ($\sigma=4\%$),VC ($\sigma=2\%$),VC ($\sigma=1\%$),VC (No PDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC. VC uses the minhash algorithm for Level-2.}
  \label{fig-exbin-efficiency-graph2}
\end{figure}

### 2013-08-02 snapshot_system/failover.tex
updated plots

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_2$, $N_1$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

}
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}

\comments{

Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
nodes fail for different amounts of sharing of filesystem blocks in the index.
We show 6.3 for the VO sharing because that is what we measured in our dataset,
and while we expect it to continue to grow (thereby decreasing fault
tolerance), it should do so slowly. for VC we use 1250, because that is what we
estimate at 2500 VMs based on the linear growth up to 105 VMs. We also show
2500 VMs sharing each PDS FSB because that is the absolute worst case for 2500
VMs. Our results show that even the VC worst case provides better VM
reliability than our optimistic amount of sharing in VO. 
The key factor placed is that  $N_1 +N_2 <
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig:pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. We
use our estimate of 1250 VMs sharing each PDS block, which is what we expect
for 2500 VMs, given the growth up to 105 VMs. It is easy to see though thatr
increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. Increasing the
PDS replication is cheap because is makes up a very small percent of the
stored data, but the impact is significant. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,1250$ (estimated)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,6.3$ (optimistic)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig:vm-availability}
\end{figure}

\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1250)}
  \label{fig:pds-replication}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig:pds-replication2}
\end{figure}

}

>>>>

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                width=\linewidth,
                height=0.7\linewidth,
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.7\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_2$, $N_1$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

}
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.7\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}
